NIRCam Calibration Plan

### 2016-12-21 ms.tex
I added more description of the cluster selection criteria.

Our team examined open clusters from the WEBDA database\footnote{https://www.univie.ac.at/webda/webda.html} to find clusters most suitable for flux calibration with solar-like stars.
The parameters under consideration were the the following:
\begin{itemize}
\item {\bf Age:} For the methods to work, the solar-mass stars must be on the main sequence. If we require that a solar mass star have $T_{\rm eff}$ = 5780 +/- 100 K, the cluster would have to be between 0.3 Gyr and 10 Gyr using Dartmouth evolutionary models \citep{dotter2008dartmouth}. Furthermore, the age should be $\lesssim$7 Gyr to avoid main sequence turnoff of near-solar stars.
\item {\bf Extinction} Extinction should be as small as possible to minimize the effects of extinction correction to photometry. Of the clusters found, E(B-V) $\lesssim < 0.1$.
\item {\bf Distance Modulus} The cluster must be distant enough to not saturate NIRCam's wide filters in full frame mode. The most easily saturated filter for G stars is the F090W, which corresponds to a G2~V star of 15.9. This means the distance modulus should be 12.6 for a solar absolute K=3.28 \citep{binney1998book}.
The longer wide band filters (F200W, F277W, F356W, and F444W) will not saturate for a distance modulus larger than 11.8.
\textcolor{red}{Calculate with extinction!}
\item {\bf Metallicity}
\item {\bf Compactness}
\item {\bf Ancillary data}
\end{itemize}

>>>>

Our team examined open clusters from the WEBDA database\footnote{https://www.univie.ac.at/webda/webda.html} to find clusters most suitable for flux calibration with solar-like stars.
The parameters under consideration were the the following:
\begin{itemize}
\item {\bf Age:} For the methods to work, the solar-mass stars must be on the main sequence. If we require that a solar mass star have $T_{\rm eff}$ = 5780 +/- 100 K, the cluster would have to be between 0.3 Gyr and 10 Gyr using Dartmouth evolutionary models \citep{dotter2008dartmouth}. Furthermore, the age should be $\lesssim$7 Gyr to avoid main sequence turnoff of near-solar stars.
\item {\bf Extinction} Extinction should be as small as possible to minimize the effects of extinction correction to photometry. Of the clusters found, E(B-V) $\lesssim < 0.1$.
\item {\bf Distance Modulus} The cluster must be distant enough to not saturate NIRCam's wide filters in full frame mode. The most easily saturated filter for G stars is the F090W, which corresponds to a G2~V star of 15.9. This means the distance modulus should be 12.6 for a solar absolute K=3.28 \citep{binney1998book}.
The longer wide band filters (F200W, F277W, F356W, and F444W) will not saturate for a distance modulus larger than 11.8.
\textcolor{red}{Calculate with extinction!}
\item {\bf Metallicity} Ideally, the cluster should have near-solar metallicity. NGC 2420 and NGC 6811 have -0.08 $<=$ [Fe/H] $<=$ 0.05. NGC 2506, is metal poor at [Fe/H]=-0.32.
\item {\bf Compactness} The cluster should be relatively compact compared to NIRCam's FOV (2'$\times$2' per module). We selected clusters $\lesssim 15\arcmin$
\item {\bf Ancillary data} The clusters should have ancillary photometry from multiple observatories for cross-calibration. We preferred clusters with 2MASS, WISE and IRAC measurements.
\item {\bf Visibility} The clusters should be spread out to ensure that at least one is visible during the commissioning period.
\end{itemize}

With all these considerations in play, we selected NGC 2420 as the best fit for the multiple criteria.
NGC 2506 and NGC 6811 are next-best fits and have somewhat complimentary visibility windows, visible in Figure \ref{fig:clusterVis}.
